Effective Dynamic Models of Metabolic Networks

### 2016-03-08 Paper_v1.tex
1st Intro Paragraph Update

>>>>

The advent of new and creative approaches to the mathematical modeling of cell metabolism allows for the accurate description and prediction of cell behavior for a wide variety of organism and culture conditions.  Monod kinetics have traditionally been used as unstructured models to describe cell growth, substrate consumption, and product formation [REF].  Structured models of metabolic pathways, such as Flux Balance Analysis (FBA), attempt to describe cellular behavior using the stoichiometry of biochemical networks, a pseudo-steady state assumption, an objective function, and system constraints [REF].  Cybernetic modeling approaches cell metabolism as a resource optimization problem; control variables are used to direct the allocation of resources through the cell in a manner most favorable to cell survival, growth, and product formation (Ramkrishna \& Song, 2012). Dynamic Flux Balance Analysis couples FBA with dynamic or static optimization methods to describe the change in metabolic fluxes over time (Mahadevan et al. 2002).
